Open archaeology, open source?

### 2024-04-15 analysis/_99-appendices.qmd
Fix link

The results presented here are based on the directory of open archaeology projects maintained at <https://open-archaeo.info> [@batist2023].
The specific version we used is available from Zenodo at <https://doi.org/10.5281/zenodo.10625236> as well as in the compendium associated with this paper [@roe2024, https://doi.org/10.5281/zenodo.8393043], in CSV format under `analysis/raw_data`.

>>>>

The results presented here are based on the directory of open archaeology projects maintained at <https://open-archaeo.info> [@batist2023].
The specific version we used is available from Zenodo at <https://doi.org/10.5281/zenodo.10625236> as well as in the compendium associated with this paper [@roe2024, <https://doi.org/10.5281/zenodo.8393043>], in CSV format under `analysis/raw_data`.
